% NO \documentclass
% NO \usepackage
% NO \begin{document}
\newpage

% ============================================================
% HEADER: enabled here for all pages of this chapter
% ============================================================
\fancyhead[L]{\fontsize{10}{12}\selectfont Chapter 2: Product Backlog Planning}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
\pagestyle{fancy}

% First page of chapter: no header, page number only
\thispagestyle{plain}

% ============================================================
%  TABLE OF CONTENTS ENTRIES
% ============================================================
\phantomsection
\addcontentsline{toc}{chapter}{Chapter 2: Product Backlog Planning}

% ============================================================
%  CHAPTER TITLE
% ============================================================
\begin{center}
  {\fontsize{20}{24}\selectfont \textbf{Chapter 2}}
\end{center}

\noindent\rule{\textwidth}{0.4pt}

\vspace{0.3cm}

\begin{center}
  {\fontsize{20}{24}\selectfont \textbf{Product Backlog Planning}}
\end{center}

\vspace{0.6cm}

% ============================================================
%  INTRODUCTION
% ============================================================
\ReportSection{Introduction}{Introduction}

{\fontsize{12}{16}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent This chapter defines the product backlog planning for the proposed internal platform at ArabSoft. It identifies the actors, structures the functional and non-functional requirements, and formalizes user stories and backlog priorities that will guide sprint planning and implementation.

}

\vspace{6pt}

% ============================================================
%  I. ACTOR IDENTIFICATION
% ============================================================
\ReportSection{I. Actor Identification}{I. Actor Identification}

\ReportSubsection{I.1 Employee}{\hspace{0.5cm} 1. Employee}

{\fontsize{12}{18}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent The employee submits administrative requests, tracks processing status, accesses assigned tasks, and receives notifications related to approvals, rejections, and project activities.

}

\vspace{6pt}

\ReportSubsection{I.2 Team Leader}{\hspace{0.5cm} 2. Team Leader}

{\fontsize{12}{18}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent The team leader supervises team activities, validates requests requiring managerial approval, assigns and follows tasks, and monitors project execution indicators.

}

\vspace{6pt}

\ReportSubsection{I.3 HR Manager}{\hspace{0.5cm} 3. HR Manager}

{\fontsize{12}{18}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent The HR manager manages employee records and roles, performs final validation of administrative requests, and monitors compliance through dashboards and reports.

}

\vspace{6pt}

\ReportSubsection{I.4 New User}{\hspace{0.5cm} 4. New User}

{\fontsize{12}{18}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent A new user is registered in the platform but remains in a restricted state until HR validation and role assignment are completed.

}

\vspace{6pt}

% ============================================================
%  II. FUNCTIONAL REQUIREMENTS
% ============================================================
\ReportSection{II. Functional Requirements}{II. Functional Requirements}

\ReportSubsection{II.1 Authentication and access management}{\hspace{0.5cm} 1. Authentication and access management}

{\fontsize{12}{18}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent The system shall support registration, secure authentication, logout, account activation by HR, and role-based access control according to user profile.

}

\vspace{6pt}

\ReportSubsection{II.2 Administrative request management}{\hspace{0.5cm} 2. Administrative request management}

{\fontsize{12}{18}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent The platform shall manage submission, validation, rejection, and history tracking for leave requests, document requests, loan requests, and authorization requests.

}

\vspace{6pt}

\ReportSubsection{II.3 Team and employee management}{\hspace{0.5cm} 3. Team and employee management}

{\fontsize{12}{18}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent The system shall provide profile management, team assignment, leader designation, and maintenance of employee administrative information.

}

\vspace{6pt}

\ReportSubsection{II.4 Project and task management}{\hspace{0.5cm} 4. Project and task management}

{\fontsize{12}{18}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent The platform shall support project creation, task assignment, workload organization, progress tracking, and status visibility for all authorized stakeholders.

}

\vspace{6pt}

\ReportSubsection{II.5 Notification and reporting}{\hspace{0.5cm} 5. Notification and reporting}

{\fontsize{12}{18}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent The system shall send operational notifications and provide reports and dashboards to support monitoring, traceability, and decision-making.

}

\vspace{6pt}

\ReportSubsection{II.6 AI assistance and decision support}{\hspace{0.5cm} 6. AI assistance and decision support}

{\fontsize{12}{18}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent The platform shall provide AI-assisted support to help employees prepare administrative requests, assist team leaders in reviewing requests and workload constraints, and support HR managers with recommendation-oriented decision assistance while preserving human validation, traceability, and auditability.

}

\vspace{6pt}

% ============================================================
%  III. NON-FUNCTIONAL REQUIREMENTS
% ============================================================
\ReportSection{III. Non-Functional Requirements}{III. Non-Functional Requirements}

\ReportSubsection{III.1 Security}{\hspace{0.5cm} 1. Security}

{\fontsize{12}{18}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent The application must guarantee secure authentication, protection of sensitive data, strict role-based permissions, and complete audit traceability.

}

\vspace{6pt}

\ReportSubsection{III.2 Performance}{\hspace{0.5cm} 2. Performance}

{\fontsize{12}{18}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent The platform must maintain acceptable response times under expected internal usage and support concurrent request processing without significant delays.

}

\vspace{6pt}

\ReportSubsection{III.3 Usability}{\hspace{0.5cm} 3. Usability}

{\fontsize{12}{18}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent Interfaces must be clear and intuitive to reduce training effort and facilitate adoption by employees, team leaders, and HR managers.

}

\vspace{6pt}

\ReportSubsection{III.4 Maintainability}{\hspace{0.5cm} 4. Maintainability}

{\fontsize{12}{18}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent The system architecture must allow efficient correction, enhancement, and extension through modular and well-documented components.

}

\vspace{6pt}

\ReportSubsection{III.5 Scalability}{\hspace{0.5cm} 5. Scalability}

{\fontsize{12}{18}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent The platform should support future growth in users, workflows, and modules without requiring major redesign.

}

\vspace{6pt}

% ============================================================
%  IV. USER STORIES
% ============================================================
\ReportSection{IV. User Stories}{IV. User Stories}

% Reusable user-story card component and 3-column grid helpers
\definecolor{empfill}{RGB}{252,236,238}
\definecolor{empborder}{RGB}{220,158,165}
\definecolor{leadfill}{RGB}{235,244,253}
\definecolor{leadborder}{RGB}{153,187,219}
\definecolor{hrfill}{RGB}{236,248,236}
\definecolor{hrborder}{RGB}{156,198,158}

\newcommand{\storycard}[3]{%
  \begin{tikzpicture}
    \node[
      draw=#2,
      fill=#1,
      rounded corners=3mm,
      line width=0.35pt,
      inner sep=8pt,
      text width=0.27\textwidth,
      minimum height=3.7cm,
      align=left,
      anchor=north
    ] {\fontsize{10.5}{13}\selectfont #3};
  \end{tikzpicture}%
}

\newcommand{\storyrow}[3]{%
  \noindent\begin{tabular}{m{0.32\textwidth}m{0.32\textwidth}m{0.32\textwidth}}
    \centering #1 & \centering #2 & \centering #3
  \end{tabular}\par\vspace{8pt}%
}

\newcommand{\storyempty}{\mbox{}}

\ReportSubsection{IV.1 Employee User Stories}{\hspace{0.5cm} 1. Employee User Stories}

\vspace{4pt}
\begin{center}
  {\fontsize{13}{16}\selectfont \textbf{Employee User Stories}}
\end{center}
\vspace{4pt}

\storyrow
{\storycard{empfill}{empborder}{As an employee, I want to sign in securely so that I can access the platform according to my role.}}
{\storycard{empfill}{empborder}{As an employee, I want to sign out securely so that I can protect my account after use.}}
{\storycard{empfill}{empborder}{As an employee, I want to manage my profile information so that my personal data stays accurate.}}

\storyrow
{\storycard{empfill}{empborder}{As an employee, I want to change my password securely so that I can keep my account protected.}}
{\storycard{empfill}{empborder}{As an employee, I want to access my personal dashboard so that I can quickly view the most relevant information.}}
{\storycard{empfill}{empborder}{As an employee, I want to submit and cancel a leave request before decision so that my leave workflow stays accurate.}}

\storyrow
{\storycard{empfill}{empborder}{As an employee, I want to submit a document request so that I can obtain official HR documents.}}
{\storycard{empfill}{empborder}{As an employee, I want to submit a loan request so that I can ask for financial support through the platform.}}
{\storycard{empfill}{empborder}{As an employee, I want to submit an authorization request so that I can formalize exceptional permissions.}}

\storyrow
{\storycard{empfill}{empborder}{As an employee, I want to track request status and history so that I can follow leave and administrative workflows.}}
{\storycard{empfill}{empborder}{As an employee, I want to view my assigned tasks and project calendar so that I can organize my work efficiently.}}
{\storycard{empfill}{empborder}{As an employee, I want to filter tasks by project so that I can focus on the work context concerned.}}

\storyrow
{\storycard{empfill}{empborder}{As an employee, I want to receive notifications and emails about role, request, leave, and task updates so that I stay informed.}}
{\storyempty}
{\storyempty}

\vspace{8pt}

\ReportSubsection{IV.2 Team Leader User Stories}{\hspace{0.5cm} 2. Team Leader User Stories}

\vspace{4pt}
\begin{center}
  {\fontsize{13}{16}\selectfont \textbf{Team Leader User Stories}}
\end{center}
\vspace{4pt}

\storyrow
{\storycard{leadfill}{leadborder}{As a team leader, I want to sign in securely so that I can access the platform according to my role.}}
{\storycard{leadfill}{leadborder}{As a team leader, I want to sign out securely so that I can protect my account after use.}}
{\storycard{leadfill}{leadborder}{As a team leader, I want to manage my profile information so that my personal data stays accurate.}}

\storyrow
{\storycard{leadfill}{leadborder}{As a team leader, I want to change my password securely so that I can keep my account protected.}}
{\storycard{leadfill}{leadborder}{As a team leader, I want to access my dashboard so that I can quickly monitor team activity.}}
{\storycard{leadfill}{leadborder}{As a team leader, I want to review team leave requests so that I can process them according to team constraints.}}

\storyrow
{\storycard{leadfill}{leadborder}{As a team leader, I want to approve or reject leave requests with a reason so that decisions remain clear and traceable.}}
{\storycard{leadfill}{leadborder}{As a team leader, I want to monitor team workload so that I can balance responsibilities effectively.}}
{\storycard{leadfill}{leadborder}{As a team leader, I want to assign tasks to team members so that project work is distributed properly.}}

\storyrow
{\storycard{leadfill}{leadborder}{As a team leader, I want to follow task progress and receive completion notifications so that I can monitor delivery.}}
{\storycard{leadfill}{leadborder}{As a team leader, I want to view the team leave calendar within my scope so that I can anticipate availability issues.}}
{\storycard{leadfill}{leadborder}{As a team leader, I want to use employee-side leave and request actions for my own needs so that personal workflows remain consistent.}}

\vspace{8pt}

\ReportSubsection{IV.3 HR Manager User Stories}{\hspace{0.5cm} 3. HR Manager User Stories}

\vspace{4pt}
\begin{center}
  {\fontsize{13}{16}\selectfont \textbf{HR Manager User Stories}}
\end{center}
\vspace{4pt}

\storyrow
{\storycard{hrfill}{hrborder}{As an HR manager, I want to sign in securely so that I can access the platform according to my role.}}
{\storycard{hrfill}{hrborder}{As an HR manager, I want to sign out securely so that I can protect my account after use.}}
{\storycard{hrfill}{hrborder}{As an HR manager, I want to manage my profile information so that my personal data stays accurate.}}

\storyrow
{\storycard{hrfill}{hrborder}{As an HR manager, I want to change my password securely so that I can keep my account protected.}}
{\storycard{hrfill}{hrborder}{As an HR manager, I want to access my dashboard so that I can monitor operational activity.}}
{\storycard{hrfill}{hrborder}{As an HR manager, I want to assign roles and trigger user notification so that access changes are communicated clearly.}}

\storyrow
{\storycard{hrfill}{hrborder}{As an HR manager, I want to activate or deactivate accounts so that access remains controlled.}}
{\storycard{hrfill}{hrborder}{As an HR manager, I want to manage employee administrative information so that records stay complete and accurate.}}
{\storycard{hrfill}{hrborder}{As an HR manager, I want to make final decisions on leave and administrative requests so that workflows are completed properly.}}

\storyrow
{\storycard{hrfill}{hrborder}{As an HR manager, I want to manage teams and team leaders so that the organizational structure remains consistent.}}
{\storycard{hrfill}{hrborder}{As an HR manager, I want broad leave calendar visibility and filters so that I can supervise teams, employees, dates, and statuses.}}
{\storycard{hrfill}{hrborder}{As an HR manager, I want to consult login history and available audit traces so that system activity remains supervised.}}

\storyrow
{\storycard{hrfill}{hrborder}{As an HR manager, I want to upload official request files and notify users so that final HR outputs are communicated.}}
{\storycard{hrfill}{hrborder}{As an HR manager, I want to trace request history and cancellations before decision so that workflow follow-up remains clear.}}
{\storyempty}

% ============================================================
%  V. PRODUCT BACKLOG
% ============================================================
  \ReportSection{V. Product Backlog}{V. Product Backlog}

\vspace{0.15cm}

{\fontsize{11}{15}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent The product backlog is organized into six functional sprints. Each sprint groups related features according to business value and implementation logic, from platform access and request workflows to HR administration, project tracking, and AI-assisted support.

}

\vspace{0.15cm}
\small
\renewcommand{\arraystretch}{1.18}
\setlength{\tabcolsep}{3.2pt}
\setlength{\LTleft}{-0.6cm}
\newcommand{\BacklogSprintPageGuard}{\Needspace{0.80\textheight}}
\newcommand{\BacklogNextSprintTable}{%
  \par
  \BacklogSprintPageGuard
  \par
}
\newcommand{\BacklogContinuedCaption}{\caption*{Table \ref{tab:product_backlog}: Product Backlog (continued)}}

% ---------- Sprint 1 ----------
\BacklogSprintPageGuard
\begin{longtable}{|>{\centering\bfseries}m{2.55cm}|>{\centering\bfseries}m{0.8cm}|>{\centering\bfseries}m{2.8cm}|m{7cm}|>{\centering\arraybackslash}m{1.55cm}|}
\hline
\rowcolor{blue!20}
\textbf{Sprint} & \textbf{Num} & \textbf{User Story} & \centering\textbf{Description} & {\scriptsize\textbf{Complexity}} \\
\hline
\endfirsthead
\hline
\rowcolor{blue!20}
\textbf{Sprint} & \textbf{Num} & \textbf{User Story} & \centering\textbf{Description} & {\scriptsize\textbf{Complexity}} \\
\hline
\endhead
\endfoot
\endlastfoot
\multirow{11}{=}{\centering\textbf{Sprint 1\\[4pt] Access}}
& US 1 & Registration & As a new user, I want to create an account so that I can request platform access. & Medium \\
\cline{2-5}
& US 2 & Secure login & As a user, I want to sign in securely so that I can access the platform according to my role. & Low \\
\cline{2-5}
& US 3 & Logout & As a user, I want to sign out securely so that I can protect my account after use. & Low \\
\cline{2-5}
& US 4 & Password reset & As a user, I want to reset my password securely so that I can recover access. & Medium \\
\cline{2-5}
& US 5 & Profile update & As a user, I want to update my profile so that my personal data stays accurate. & Low \\
\cline{2-5}
& US 6 & NEW\_USER restriction & As an HR manager, I want new users to remain restricted until HR validation. & High \\
\cline{2-5}
& US 7 & Role assignment & As an HR manager, I want to assign roles so that each user receives the correct access rights. & Medium \\
\cline{2-5}
& US 8 & Role assignment notification and email & As a user, I want to receive a notification and email when my role is assigned. & Low \\
\cline{2-5}
& US 9 & Account activation & As an HR manager, I want to activate approved accounts so that validated users can access the platform. & Medium \\
\cline{2-5}
& US 10 & Account deactivation & As an HR manager, I want to deactivate accounts so that access can be revoked when needed. & Medium \\
\cline{2-5}
& US 11 & Login history & As an HR manager, I want to consult login history so that authentication activity can be traced. & Medium \\
\hline

\end{longtable}

\BacklogNextSprintTable

\begin{longtable}{|>{\centering\bfseries}m{2.55cm}|>{\centering\bfseries}m{0.8cm}|>{\centering\bfseries}m{2.8cm}|m{7cm}|>{\centering\arraybackslash}m{1.55cm}|}
\hline
\rowcolor{blue!20}
\textbf{Sprint} & \textbf{Num} & \textbf{User Story} & \centering\textbf{Description} & {\scriptsize\textbf{Complexity}} \\
\hline
\endfirsthead
\hline
\rowcolor{blue!20}
\textbf{Sprint} & \textbf{Num} & \textbf{User Story} & \centering\textbf{Description} & {\scriptsize\textbf{Complexity}} \\
\hline
\endhead
\endfoot
\endlastfoot
\multirow{10}{=}{\centering\textbf{Sprint 2\\[4pt] Leave\\Management}}
& US 12 & Leave submission & As an employee, I want to submit a leave request so that I can ask for time off through a structured workflow. & Medium \\
\cline{2-5}
& US 13 & Leave tracking & As an employee, I want to track my leave request status so that I can follow its progress. & Low \\
\cline{2-5}
& US 14 & Leave history & As an employee, I want to view my leave history so that I can review my previous leave requests in one place. & Low \\
\cline{2-5}
& US 15 & Team review & As a team leader, I want to review team leave requests before making a decision. & Medium \\
\cline{2-5}
& US 16 & Team approval & As a team leader, I want to approve leave requests so that valid requests can move forward in the workflow. & Medium \\
\cline{2-5}
& US 17 & Team rejection with reason & As a team leader, I want to reject leave requests with a reason so that the decision remains traceable. & Medium \\
\cline{2-5}
& US 18 & HR final decision & As an HR manager, I want to make the final decision on leave requests so that the workflow is completed properly. & High \\
\cline{2-5}
& US 19 & Leave cancellation before decision & As an employee, I want to cancel a leave request before a decision is taken so that I can withdraw an unnecessary request. & Low \\
\cline{2-5}
& US 20 & Leave decision notifications and emails & As an employee, I want notifications and emails about leave approvals or rejections. & Low \\
\cline{2-5}
& US 21 & Team leader personal leave actions & As a team leader, I want to submit and follow my own leave requests as an employee so that my personal requests follow the same workflow. & Low \\
\hline

\end{longtable}

\BacklogNextSprintTable

\begin{longtable}{|>{\centering\bfseries}m{2.55cm}|>{\centering\bfseries}m{0.8cm}|>{\centering\bfseries}m{2.8cm}|m{7cm}|>{\centering\arraybackslash}m{1.55cm}|}
\hline
\rowcolor{blue!20}
\textbf{Sprint} & \textbf{Num} & \textbf{User Story} & \centering\textbf{Description} & {\scriptsize\textbf{Complexity}} \\
\hline
\endfirsthead
\hline
\rowcolor{blue!20}
\textbf{Sprint} & \textbf{Num} & \textbf{User Story} & \centering\textbf{Description} & {\scriptsize\textbf{Complexity}} \\
\hline
\endhead
\endfoot
\endlastfoot
\multirow{10}{=}{\centering\textbf{Sprint 3\\[4pt] Administrative\\Requests}}
& US 22 & Document submission & As an employee, I want to submit a document request so that I can obtain official HR documents through the platform. & Medium \\
\cline{2-5}
& US 23 & Loan submission & As an employee, I want to submit a loan request so that I can ask for financial support through a structured workflow. & Medium \\
\cline{2-5}
& US 24 & Authorization submission & As an employee, I want to submit an authorization request so that I can formalize exceptional permissions. & Medium \\
\cline{2-5}
& US 25 & Request tracking & As an employee, I want to track the status of my administrative requests so that I can follow their progress. & Low \\
\cline{2-5}
& US 26 & Request history & As an employee, I want to view my administrative request history so that I can consult previous submissions. & Low \\
\cline{2-5}
& US 27 & HR final decision & As an HR manager, I want to make the final decision on administrative requests so that each request receives an official outcome. & High \\
\cline{2-5}
& US 28 & Official file upload & As an HR manager, I want to upload finalized files so that approved requests include official documents. & Medium \\
\cline{2-5}
& US 29 & Request status notifications and emails & As a user, I want notifications and emails about request status changes and decisions. & Low \\
\cline{2-5}
& US 30 & Request cancellation before decision & As an employee, I want to cancel an administrative request before a decision is taken so that I can withdraw it when it is no longer needed. & Low \\
\cline{2-5}
& US 31 & Team leader personal request actions & As a team leader, I want to submit and follow my own administrative requests as an employee so that my personal requests follow the same logic. & Low \\
\hline

\end{longtable}

\BacklogNextSprintTable

\begin{longtable}{|>{\centering\bfseries}m{2.55cm}|>{\centering\bfseries}m{0.8cm}|>{\centering\bfseries}m{2.8cm}|m{7cm}|>{\centering\arraybackslash}m{1.55cm}|}
\hline
\rowcolor{blue!20}
\textbf{Sprint} & \textbf{Num} & \textbf{User Story} & \centering\textbf{Description} & {\scriptsize\textbf{Complexity}} \\
\hline
\endfirsthead
\hline
\rowcolor{blue!20}
\textbf{Sprint} & \textbf{Num} & \textbf{User Story} & \centering\textbf{Description} & {\scriptsize\textbf{Complexity}} \\
\hline
\endhead
\endfoot
\endlastfoot
\multirow{10}{=}{\centering\textbf{Sprint 4\\[4pt] HR Management\\\& Calendar}}
& US 32 & Employee records & As an HR manager, I want to manage employee information so that records stay accurate. & Medium \\
\cline{2-5}
& US 33 & Team management & As an HR manager, I want to manage teams so that the organizational structure remains consistent. & Medium \\
\cline{2-5}
& US 34 & Team leader assignment & As an HR manager, I want to assign team leaders so that each team has the correct supervisor. & Medium \\
\cline{2-5}
& US 35 & Role management & As an HR manager, I want to manage roles so that access rights match responsibilities. & Medium \\
\cline{2-5}
& US 36 & HR dashboard & As an HR manager, I want to access an HR dashboard so that I can monitor operational activity at a glance. & Medium \\
\cline{2-5}
& US 37 & Login history and audit traces & As an HR manager, I want to review login history and available audit traces. & Medium \\
\cline{2-5}
& US 38 & Team leave calendar view & As a team leader, I want to view the leave calendar within my team scope so that I can plan availability. & Medium \\
\cline{2-5}
& US 39 & Leave calendar filters & As a team leader or HR manager, I want to filter leave information by employee, status, and date so that calendar views stay focused. & Low \\
\cline{2-5}
& US 40 & HR leave calendar view & As an HR manager, I want broader leave visibility across teams and employees so that I can supervise planning. & Medium \\
\cline{2-5}
& US 41 & Request traceability & As an HR manager, I want to trace request history so that each workflow decision remains auditable. & Medium \\
\hline

\end{longtable}

\BacklogNextSprintTable

\begin{longtable}{|>{\centering\bfseries}m{2.55cm}|>{\centering\bfseries}m{0.8cm}|>{\centering\bfseries}m{2.8cm}|m{7cm}|>{\centering\arraybackslash}m{1.55cm}|}
\hline
\rowcolor{blue!20}
\textbf{Sprint} & \textbf{Num} & \textbf{User Story} & \centering\textbf{Description} & {\scriptsize\textbf{Complexity}} \\
\hline
\endfirsthead
\hline
\rowcolor{blue!20}
\textbf{Sprint} & \textbf{Num} & \textbf{User Story} & \centering\textbf{Description} & {\scriptsize\textbf{Complexity}} \\
\hline
\endhead
\endfoot
\endlastfoot
\multirow{11}{=}{\centering\textbf{Sprint 5\\[4pt] Projects and\\Tasks}}
& US 42 & Project creation & As a team leader, I want to create projects so that I can organize work around clear objectives. & Medium \\
\cline{2-5}
& US 43 & Project list & As a user, I want to view the project list so that I can access the projects relevant to me. & Low \\
\cline{2-5}
& US 44 & Task creation & As a team leader, I want to create tasks so that project work can be broken into manageable actions. & Medium \\
\cline{2-5}
& US 45 & Task assignment & As a team leader, I want to assign tasks to team members so that project work is distributed properly. & Medium \\
\cline{2-5}
& US 46 & Task status update & As an assignee, I want to update task status so that task progress remains visible to the team. & Low \\
\cline{2-5}
& US 47 & Task tracking & As a user, I want to track task status so that I can monitor progress toward completion. & Medium \\
\cline{2-5}
& US 48 & Project/task dashboard & As a team leader, I want a project and task dashboard so that I can monitor delivery. & Medium \\
\cline{2-5}
& US 49 & Project and task calendar view & As a user, I want to view project and task dates in a calendar so that planning information is easier to follow. & Medium \\
\cline{2-5}
& US 50 & Project-based task filters & As a user, I want to filter tasks by project so that I can focus on a specific work context. & Low \\
\cline{2-5}
& US 51 & Assignee task assignment notification and email & As an assignee, I want a notification and email when a task is assigned to me. & Low \\
\cline{2-5}
& US 52 & Team leader task completion notification and email & As a team leader, I want a notification and email when a task is completed. & Low \\
\hline

\end{longtable}

\BacklogNextSprintTable

\begin{longtable}{|>{\centering\bfseries}m{2.55cm}|>{\centering\bfseries}m{0.8cm}|>{\centering\bfseries}m{2.8cm}|m{7cm}|>{\centering\arraybackslash}m{1.55cm}|}
\hline
\rowcolor{blue!20}
\textbf{Sprint} & \textbf{Num} & \textbf{User Story} & \centering\textbf{Description} & {\scriptsize\textbf{Complexity}} \\
\hline
\endfirsthead
\hline
\rowcolor{blue!20}
\textbf{Sprint} & \textbf{Num} & \textbf{User Story} & \centering\textbf{Description} & {\scriptsize\textbf{Complexity}} \\
\hline
\endhead
\endfoot
\endlastfoot
\multirow{10}{=}{\centering\textbf{Sprint 6\\[4pt] AI Assistance\\\& Decision\\Support}}
& US 53 & AI request assistant & As an employee, I want an AI request assistant so that I can get guided help while preparing a request. & Medium \\
\cline{2-5}
& US 54 & AI leave drafting & As an employee, I want AI assistance to draft my leave request so that I can prepare it faster before confirming submission. & Medium \\
\cline{2-5}
& US 55 & AI document drafting & As an employee, I want AI assistance to draft my document request so that I can submit a clearer request after confirmation. & Medium \\
\cline{2-5}
& US 56 & AI loan drafting & As an employee, I want AI assistance to draft my loan request so that I can structure my request before confirming it. & Medium \\
\cline{2-5}
& US 57 & AI authorization drafting & As an employee, I want AI assistance to draft my authorization request so that I can prepare the request before submitting it. & Medium \\
\cline{2-5}
& US 58 & TL request summary & As a team leader, I want AI to summarize requests so that I can review them faster before making a human decision. & Medium \\
\cline{2-5}
& US 59 & TL workload hints & As a team leader, I want AI workload and conflict hints so that I can detect scheduling risks before validating team requests. & Medium \\
\cline{2-5}
& US 60 & TL reassignment suggestions & As a team leader, I want AI suggestions for task reassignment so that I can balance workload more effectively. & Medium \\
\cline{2-5}
& US 61 & HR recommendation support & As an HR manager, I want AI recommendation support so that I can review requests with decision assistance. & High \\
\cline{2-5}
& US 62 & Explanation and traceability & As a team leader or HR manager, I want AI explanations and traceability so that every suggestion remains understandable and auditable. & High \\
\hline
\BacklogContinuedCaption
\end{longtable}

\normalsize
\setlength{\tabcolsep}{6pt}

\vspace{6pt}

% ============================================================
%  VI. RELEASE ORGANIZATION
% ============================================================
\Needspace{24\baselineskip}
\ReportSection{VI. Release Organization}{VI. Release Organization}

{\fontsize{12}{18}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent The six planned sprints are grouped into three major releases to ensure progressive and coherent delivery of the platform.

}

\begin{figure}[H]
\centering
\begin{tikzpicture}[
  x=1cm,
  y=1cm,
  font=\fontsize{7.4}{8.6}\selectfont,
  planbox/.style={
    draw=black!70,
    fill=cyan!18,
    line width=0.32pt,
    align=center,
    inner sep=2pt
  },
  releasebox/.style={
    planbox,
    minimum width=2.62cm,
    minimum height=0.78cm,
    text width=2.35cm,
    font=\fontsize{7.4}{8.5}\selectfont\bfseries
  },
  sprintbox/.style={
    planbox,
    minimum width=2.54cm,
    minimum height=0.92cm,
    text width=2.28cm,
    font=\fontsize{6.95}{8.2}\selectfont\bfseries
  },
  tag/.style={
    draw=black!70,
    fill=white,
    line width=0.28pt,
    minimum width=1.02cm,
    minimum height=0.24cm,
    inner sep=1pt,
    align=center,
    font=\fontsize{6.25}{7.1}\selectfont\bfseries
  },
  connector/.style={
    draw=yellow!75!black,
    line width=0.32pt,
    line cap=round
  }
]

\draw[line width=0.38pt, draw=black] (0.00,0.05) rectangle (14.95,-4.08);

\node[releasebox] (r1) at (1.30,-0.55) {Core\\Foundation};
\node[releasebox] (r2) at (6.35,-0.50) {Workflow\\Management};
\node[releasebox] (r3) at (11.55,-0.55) {Advanced Support\\and Intelligence};

\node[tag] (rt1) at (1.75,-0.91) {Release 1};
\node[tag] (rt2) at (6.80,-0.86) {Release 2};
\node[tag] (rt3) at (12.00,-0.91) {Release 3};

\node[sprintbox] (s1) at (3.15,-2.08) {Access};
\node[sprintbox] (s2) at (4.20,-3.18) {Leave\\Management};

\node[sprintbox] (s3) at (8.30,-1.78) {Administrative\\Requests};
\node[sprintbox] (s4) at (8.20,-3.22) {HR Management\\and Calendar};

\node[sprintbox] (s5) at (13.40,-1.78) {Projects\\and Tasks};
\node[sprintbox] (s6) at (13.45,-3.22) {AI Assistance\\and Decision\\Support};

\node[tag] at (3.75,-2.48) {Sprint 1};
\node[tag] at (4.80,-3.58) {Sprint 2};
\node[tag] at (8.90,-2.18) {Sprint 3};
\node[tag] at (8.80,-3.62) {Sprint 4};
\node[tag] at (14.00,-2.18) {Sprint 5};
\node[tag] at (14.05,-3.62) {Sprint 6};

\draw[connector] (rt1.south) -- (1.75,-1.62) -- (1.75,-2.08) -- (s1.west);
\draw[connector] (1.75,-1.62) -- (1.75,-3.18) -- (s2.west);

\draw[connector] (rt2.south) -- (6.80,-1.48) -- (6.80,-1.78) -- (s3.west);
\draw[connector] (6.80,-1.48) -- (6.80,-3.22) -- (s4.west);

\draw[connector] (rt3.south) -- (12.00,-1.48) -- (12.00,-1.78) -- (s5.west);
\draw[connector] (12.00,-1.48) -- (12.00,-3.22) -- (s6.west);

\end{tikzpicture}
\caption{Organization of Releases}
\end{figure}

\vspace{6pt}
% ============================================================
%  CONCLUSION
% ============================================================
\ReportSection{Conclusion}{Conclusion}

{\fontsize{12}{16}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent This chapter established the backlog-planning foundation of the project through actor identification, requirement structuring, user stories, and prioritized backlog definition. It provides the planning baseline for sprint execution and the progressive realization of the platform at ArabSoft.

}
