% NO \documentclass
% NO \usepackage
% NO \begin{document}
\newpage
\thispagestyle{plain}

\phantomsection
\addcontentsline{toc}{chapter}{General Introduction}

\begin{center}
  \rule{\linewidth}{1.2pt}\\[0.4cm]
  {\fontsize{20}{24}\selectfont \textbf{General Introduction}}\\[0.5cm]
\end{center}
\vspace{0.8cm}

{\fontsize{12}{16}\selectfont
\setlength{\parindent}{1.2cm}
\setlength{\parskip}{6pt}

\indent Digital transformation has become a major strategic driver for companies seeking to improve organizational efficiency and ensure smooth management of internal processes. The centralization of administrative requests, project tracking, and internal communication represents significant challenges when operations are handled manually or in a fragmented manner. The growing complexity of internal workflows, together with the need for effective coordination between departments, makes the adoption of modern and structured digital tools essential.

\indent In this context, my work focuses on the \textbf{development of an internal platform for request, project, and task management at Arab Soft}. The objective is to design a practical and reliable solution that centralizes administrative requests, monitors projects and tasks, and improves communication between teams. By providing a global and real-time view of organizational activities, this platform aims to strengthen collaboration, improve process efficiency, and support better operational decision-making.

\indent The ambition of this project is to provide a tool that addresses current organizational needs while remaining adaptable to future evolution. Whether for handling internal requests, tracking project progress, assigning tasks, or improving information flow between stakeholders, the platform is designed as a complete and intuitive solution that integrates smoothly into existing work practices.

\indent This report presents the different phases of project realization. From requirements analysis to deployment, including design, development, and testing phases, I explain how this platform was built to meet user expectations and deliver concrete added value to the company. Particular attention is given to the methodological approach, technical choices, and implementation strategy adopted throughout the project.

\indent Through this work, I aim to contribute to the modernization of internal management practices and to the continuous improvement of organizational performance. This project represents an opportunity to rethink how administrative and project activities are managed by making them more structured, collaborative, and efficient.
}
% NO \end{document}
